### 2010-04-06 docs/introduction/introduction.tex
added references to our in-progress papers

\noindent The current version of the algorithm is described in our multilevel paper:
\begin{itemize}
\item {\em MAESTRO: An Adaptive Low Mach Number Hydrodynamics Algorithm for Stellar
  Flows,} A. Nonaka, A. S. Almgren, J. B. Bell, M. J. Lijewski, C. M. Malone,
  \& M. Zingale 2009, submitted to SIAM J. Sci. Comput. 
  (henceforth ``the multilevel paper'')
\end{itemize}

>>>>

\noindent The current version of the algorithm is described in our multilevel paper:
\begin{itemize}
\item {\em MAESTRO: An Adaptive Low Mach Number Hydrodynamics Algorithm for Stellar
  Flows,} A. Nonaka, A. S. Almgren, J. B. Bell, M. J. Lijewski, C. M. Malone,
  \& M. Zingale 2010, submitted to ApJ
  (henceforth ``the multilevel paper'')
\end{itemize}

\noindent We have two papers in preparation:
\begin{itemize}
\item {\em The Convective Phase Preceding Type Ia Supernovae,}
  M. Zingale, A. S. Almgren, J. B. Bell, C. M. Malone, A. Nonaka, \& S. E. Woosley 2010,
  in preparation (henceforth paper V)
\item {\em Multidimensional Modeling of Type I X-ray Bursts,}
  C. M. Malone, A. Nonaka, A. S. Almgren, J. B. Bell, \& M. Zingale 2010,
  in preparation (henceforth ``the XRB paper'')
\end{itemize}
